Embedding Dimension of Polyhedral Losses

### 2020-01-30 colt-20/embed-dim.tex
add 1d loss construction

\begin{definition}[Intersection graph, orderable]
Given a finite property $\gamma: \simplex \to 2^{\R}$, the \emph{intersection graph} has vertices labeled by $\R$ with an edge $(r,r')$ if $\gamma_r \cap \gamma_{r'} \cap \relint(\simplex) \neq \emptyset$, where $\relint(\simplex)$ equals the set of distributions with full support.
  A finite property $\gamma$ is \emph{orderable} if its intersection graph is a path, i.e. a connected graph where every vertex has either one or two neighbors.
\end{definition}
\jessie{Probably for appendix: compare this definition of orderable to level set intersections on hyperplane definition}
%\begin{observation}
%  A property $g$ is orderable if and only if the set $g_r \cap g_{r'}$, for $r \neq r'$, is always the intersection of a hyperplane with the simplex.
%\end{observation}

\begin{theorem}
  Let $\ell: \R \to \nonnegreals^{\Y}$ be a discrete loss.
  Then $\ell$ is $1$-embeddable if and only if there is an ordering $\R = \{r_1,\ldots,r_k\}$ of the reports such that the following two conditions hold, where $v(i)_y := : \ell(r_{i+1})_y - \ell(r_i)_y$:
  \begin{enumerate}
  \item For all $y\in\Y$, the sequence $\sgn(v(i)_y)$ is monotone in
    $i\in\{1,\ldots,k-1\}$,
  \item For all $i\in\{1,\ldots,k-2\}$, we have
    \begin{equation}
      \label{eq:1}
      \min \left\{\frac{v(i)_y}{v({i+1})_y} : v(i)_y, v({i+1})_y < 0\right\}
      \geq
      \max \left\{\frac{v(i)_y}{v({i+1})_y} : v(i)_y, v({i+1})_y > 0\right\}~.
    \end{equation}
  \end{enumerate}
\end{theorem}

>>>>

\begin{definition}[Intersection graph, orderable]
Given a finite property $\gamma: \simplex \to 2^{\R}$, the \emph{intersection graph} has vertices labeled by $\R$ with an edge $(r,r')$ if $\gamma_r \cap \gamma_{r'} \cap \relint(\simplex) \neq \emptyset$, where $\relint(\simplex)$ equals the set of distributions with full support.
  A finite property $\gamma$ is \emph{orderable} if its intersection graph is a path, i.e. a connected graph where every vertex has either one or two neighbors.
\end{definition}
\jessie{Probably for appendix: compare this definition of orderable to level set intersections on hyperplane definition}
\raf{Actually, it occurred to me that we really should use the original definition, since that's from Lambert, but we can also define the incidence graph and state (proof in appendix) that they are equivalent.}
%\begin{observation}
%  A property $g$ is orderable if and only if the set $g_r \cap g_{r'}$, for $r \neq r'$, is always the intersection of a hyperplane with the simplex.
%\end{observation}

\begin{theorem}
  Let $\ell: \R \to \nonnegreals^{\Y}$ be a discrete loss.
  Then $\ell$ is $1$-embeddable if and only if there is an ordering $\R = \{r_1,\ldots,r_k\}$ of the reports such that the following two conditions hold, where $v(i)_y := : \ell(r_i)_y - \ell(r_{i-1})_y$:
  \begin{enumerate}
  \item For all $y\in\Y$, the sequence $\sgn(v(i)_y)$ is monotone in
    $i\in\{1,\ldots,k-1\}$,
  \item For all $i\in\{2,\ldots,k-1\}$, letting
    \begin{align*}
      \lambda^-(i) &= \min \left\{\frac{v(i)_y}{v({i+1})_y} : y\in\Y, v(i)_y, v({i+1})_y < 0\right\}
      \\
      \lambda^+(i) &= \max \left\{\frac{v(i)_y}{v({i+1})_y} : y\in\Y, v(i)_y, v({i+1})_y > 0\right\}~,
    \end{align*}
    we have $\lambda^-(i) \geq \lambda^+(i)$.
  \end{enumerate}

  \raf{Still need to double check, but it will be something like this:}

  Moreover, when these conditions hold, the loss $L:\reals\to\reals^\Y$ embeds $\ell$ with $\varphi:\R\to\reals$, where
  \begin{align*}
    \varphi(r_i) &= \begin{cases}
      0 & i=1 \\
      \sum_{j=2}^i 1/\Lambda_j & i\in\{2,\ldots,k\}
    \end{cases}~,
    \\
    L(u) &= \begin{cases}
      \ell(r_1) - u K \ones & u \leq 0 \\
      \ell(r_i) + \Lambda_i \cdot (u - \varphi(r_i)) \cdot  (\ell(r_{i+1})-\ell(r_i)) & u \in [\varphi(r_i),\varphi(r_{i+1})] \\
      \ell(r_k) + u K \ones & u \geq \varphi(r_k)
    \end{cases}~,
  \end{align*}
  where $\Lambda_i := \prod_{j=2}^i \lambda(j)$ and $K=1+\max_{r\in\R,y\in\Y} |\ell(r)_y|$.
\end{theorem}
